---
title: "GloVe"
author: "Malte Söhren"
date: "12/10/2020"
output: html_document
---

```{r}
library(keras)
library(dplyr)
```

```{r}
setwd("/Users/2egaa/Desktop/nG-BotClassifier")
data <- read.csv("botornot-1.csv")
```

Select relevant variables and merge text variables. 

```{r}
data_glove <- data %>% select(c(bot, feedback, readEssayTime, readProfileTime, superspeeder))
data_glove$feedback <- as.character(data_glove$feedback)
```

Clean-up bot variable.

```{r}
data_glove$bot[is.na(data_glove$bot)] <- 0
data_glove$bot[data_glove$bot == 2] <- 1
data_glove$bot[data_glove$bot == 3] <- 1
data_glove$bot <- as.integer(data_glove$bot)
```

Read in vectors. 

```{r}
vectors <- data.table::fread('glove.6B.300d.txt', data.table = F,  encoding = 'UTF-8')
colnames(vectors) = c('word',paste('dim',1:300,sep = '_'))

as_tibble(vectors)
```


Create train & test dataset. 

```{r}
set.seed(72721)

data_train <- data_glove[1:1150,]
data_test <- data_glove[1151:1351,]
```

Set parameters.

```{r}
max_words = 1e4
maxlen = 60
dim_size = 300
```

Tokenizing.

```{r}
word_seqs <- text_tokenizer(num_words = max_words) %>% 
  fit_text_tokenizer(data_train$feedback)
```

Define training data - independent variable. 

```{r}
x_train <- texts_to_sequences(word_seqs, data_train$feedback) %>%
  pad_sequences( maxlen = maxlen) 
```

Define training data - dependent variable. 

```{r}
y_train <- as.matrix(data_train$bot)
```

Unlist word indices. 

```{r}
word_indices <- unlist(word_seqs$word_index)
```

Put them in dataframe.

```{r}
dic <- data.frame(word = names(word_indices), key = word_indices, stringsAsFactors = FALSE) %>%
  arrange(key) %>% .[1:max_words,]
```

Join the words from our corpus with the pretrained vectors.
```{r}
word_embeds <- dic  %>% left_join(vectors) %>% .[,3:302] %>% replace(., is.na(.), 0) %>% as.matrix()
```

Define and train model. 

```{r}
input <- layer_input(shape = list(maxlen), name = "input")

model <- input %>%
  layer_embedding(input_dim = max_words, output_dim = dim_size, input_length = maxlen,
                  weights = list(word_embeds), trainable = FALSE) %>%
  layer_spatial_dropout_1d(rate = 0.2 ) %>%
  bidirectional(
    layer_gru(units = 80, return_sequences = TRUE)
  )

max_pool <- model %>% layer_global_max_pooling_1d()
ave_pool <- model %>% layer_global_average_pooling_1d()

output = layer_concatenate(list(ave_pool, max_pool)) %>%
  layer_dense(units = 1, activation = "sigmoid")

model <- keras_model(input, output)

model %>% compile(
  optimizer = "adam",
  loss = "binary_crossentropy",
  metrics = c(tensorflow::tf$keras$metrics$AUC(), 'accuracy')
)

history <- model %>% keras::fit(
  x = x_train, y = y_train,
  epochs = 16,
  batch_size = 32,
  validation_split = 0.1
)
```

Define test data - indepedent variable. 

```{r}
x_test <- texts_to_sequences(word_seqs, data_test$feedback) %>%
  pad_sequences( maxlen = maxlen)
```

define test data - dependent variable.

```{r}
y_test <- as.matrix(data_test$bot)
```

Make predictions with data from testset. 

```{r}
pred <- model %>% predict(x_test)
format(round(pred, 2), scientific = FALSE)
```

Evaluate performance. 

```{r}
eval <- model %>% evaluate(x_test, y_test, verbose = 0)
```

Look at actual classes vs. predicted classes.

```{r}
newdf <- data.frame(probabilites = format(round(pred, 2)), bot = data_test$bot)
newdf
```
