---
title: "Multiclass Classification"
author: "Malte Söhren"
date: "12/16/2020"
output: html_document
---

# Loading Packages 

```{r}
library(tidyverse)
library(DataExplorer)
library(caret)
library(caretEnsemble)
library(pROC)
library(gbm)
library(data.table)
library(superml)
```

```{r}
setwd("/Users/2egaa/Desktop/ng-BotClassifier/")
data_base <- read.csv("overview_labels.csv")
```

Select relevant variables. 

```{r}
data <- data_base %>%  select(c("bot", "rejected", "freetext",  "ratioIneqUS",   "avgTime.min",    "outRatio",  "speeder", "time_1.1.1", "time_1.2.1", "time_2.1.1", "time_2.2.1", "time_2.3.1", "time_feedback", "time_feedback", "feedback"))
```

Recode target variable into three distinct classes. 

```{r}
data_tr <- setDT(data)[bot == "Human" & rejected == 1, Bot := "Slow"]
data_tr <- setDT(data)[bot == "Human" & rejected == 0, Bot := "Human"]
data_tr <- setDT(data)[bot == "Bot" & rejected == 1, Bot := "Bot"]

data_tr <- data_tr %>% select(-c("bot", "rejected"))

# 0 = no bot; 1 = slow; 2 = Bot 
```

Change classes of variables. 

```{r}
data_tr$freetext <- as.character(data_tr$freetext)
data_tr$feedback <- as.character(data_tr$feedback)
data_tr$Bot <- as.factor(data_tr$Bot)
```
Filling missing values with mean of variable.
```{r}
data_tr <- data_tr %>% 
  group_by(Bot) %>% 
  mutate(avgTime.min = ifelse(is.na(avgTime.min), mean(avgTime.min, na.rm = TRUE), 
                              avgTime.min))
```

Drop NA's.
```{r}
data_final <- data_tr %>% drop_na()
```

Create Bag-of-Words dummies. 

```{r}
cv <- CountVectorizer$new(max_features = 300, remove_stopwords = FALSE, lowercase = TRUE)

bow <- cv$fit_transform(data_final$feedback)

bow <- as.data.frame(bow)

modeldata <- bind_cols(data_final, bow)
modeldata <- modeldata %>% select(-c(feedback...292, feedback...12, freetext))


colnames(modeldata) <- make.names(colnames(modeldata))
```

# Train Models 

Split data into train and test set. 
```{r}
set.seed(64738)

cdp <- createDataPartition(modeldata$Bot, 
                               p = .7, 
                               list = FALSE, 
                               times = 1)

model_train <- modeldata[cdp,]
model_test <- modeldata[-cdp,]
```

Define control object. 

```{r}
ctrl  <- trainControl(method = "cv", 
                      number = 5,
                      summaryFunction = multiClassSummary,
                      verboseIter = TRUE,
                      classProbs = TRUE,
                      sampling = "smote",
                      savePredictions = "final")
```

# XGBoost 

Define grid. 

```{r}
grid_xg <- expand.grid(max_depth = c(2, 3),
                    nrounds = c(50, 100),
                    eta = c(0.4),
                    min_child_weight = c(1,2),
                    gamma = c(0, 0.5),
                    colsample_bytree = c(0.4, 1.0),
                    subsample = c(0, 1))
```

Train model. 

```{r}
set.seed(79647)
xgb <- train(Bot ~ .,
             data = model_train,
             method = "xgbTree",
             trControl = ctrl,
             tuneGrid = grid_xg,
             metric = "ROC")
```

Evaluate performance. 

```{r}
p_xgb <- predict(xgb, newdata = model_test, type = "raw")
cm_xgb <- confusionMatrix(p_xgb, model_test$Bot, mode = "everything", positive = "Yes")
```

# C5.0 

Train model. 

```{r}
set.seed(87543)

c5 <- train(Bot ~ .,
            data = model_train,
            method = "C5.0",
            trControl = ctrl)
```
Evaluate performance. 

```{r}
p_c5 <- predict(c5, model_test, type = "raw")
cm_c5 <- confusionMatrix(p_c5, model_test$Bot, mode = "everything", positive = "Yes")
```



